Analysis of bulk void regions

### 2014-04-20 cosmic_voids.tex
Analysis of optimal lambda_th based upon the fraction of halos

Once defined the numerical details about both classification schemes, we
shall analyse the dependence on the threshold value $\lambda_{th}$ for 
each one. In Figure \ref{fig:median_density} we calculate the median 
contrast density for cells catalogued in each one of the types of 
environment with respect to the threshold value, where filled regions 
correspond to quartiles $Q_1$ and $Q_3$ of the samples, i.e. half of the 
cells are mapped within such regions. Moreover, we calculate fraction of
halos within each one of the defined environments based upon the FOF 
catalogue of the simulation.

As was previously established by \SRKED{Hoffman et al. (2012)} and as 
can be seen in Figure \ref{fig:median_density}, the behaviour of the 
V-web scheme is significantly more sensible to variations of the 
$\lambda_{th}$ value compared with the T-web scheme. Furthermore, taking
into account the physical origin of the T-web scheme, based upon the 
Hessian matrix, environments catalogued through this scheme have a 
well-differentiate density value for all \lth range, whereas for the V-web 
case, all regions are overlapped, specially for high \lth values and for 
high density regions, being more confuse to discern a typical density for 
each type of environment. This could be explained appealing to the 
kinematic rather than dynamic origin of the V-web, which is based upon the 
velocity shear tensor, and implying that the correspondence between 
density and peculiar velocity is less trivial for high density regions, 
what it is precisely expected for the non-linear regime.

On cosmic scales, the presence of highly non-linear structures implies the 
existence of very vast regions with density lower than the mean 
cosmological value due to the mass conservation. That is why the visual 
impression of the cosmic web should be necessarily dominated by these 
under-dense regions. Keeping that in mind, our novel proposal is based upon
the correct quantification of these regions, so the optimal threshold 
value must be chosen such that: sheet regions do not invade real void 
regions (in such case, the mean density parameter of sheet regions would 
become negative) and void regions do not invade real sheet and filament 
regions (in such case, the mean density parameter of void regions would 
increase due to the contribution of over-dense regions). Thus, the optimal 
value is simply where the mean density parameter of sheet regions is 
null. According to this, we obtain the next optimal threshold values 
for the T-web and the V-web respectively, $\lambda_{opt}^T = 0.326$ and 
$\lambda_{opt}^V = 0.188$. To verify our analysis, we show in Figure 
\ref{fig:visual_impression} the visual impression for each defined critical 
value, and as can be seen, the chosen values reproduce properly the 
expected impression according to the density field.

Our classification scheme may be thought as a refinement of the recent 
schemes, where the threshold value is used to taking as a free parameter, 
based on the classic methods, where the classification is performed 
based on a cut off of the density field directly \SRKED{[references here]}.
So we make use of the objectivity achieved by the analysis of the mean 
density, but keeping all the environmental information provided by the
tensorial schemes instead of the poor description provided by the density 
field.

@@

%.........................................................................
%FIGURE 1: Median density for each environment
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/median_environments_densities_Tweb.pdf}
  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/median_environments_densities_Vweb.pdf}
  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/halos_fraction_FOF_Tweb.pdf}
  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/halos_fraction_FOF_Vweb.pdf}

@@

  \label{fig:median_density}
  \vspace{0.1 cm}

@@

%.........................................................................
%FIGURE 2: Visual impresion
\begin{flushleft}
\begin{figure*}
\begin{center}

  \captionof{figure}{\small Visual impression of the density field (left 
  panels), and of each classification scheme with the $\lambda_{th}$ values 
  obtained by our criteria (others panels). Our color convention for each 
  environment is (white) - void, (light gray) - sheet, (gray) - filament, 
  (black) - knot. For each web scheme, it has been used the previously 
  established optimal threshold as a reference value, so plots are done 
  with the next values $\lambda_{th} = 0.0$, $\lambda_{th} = 
  \lambda_{opt}/2$, $\lambda_{th} = \lambda_{opt}$ and $\lambda_{th} = 
  2\lambda_{opt}$.}

\end{center}
\end{figure*}
\end{flushleft}
%.........................................................................

%.........................................................................
%FIGURE 3: Percolation analysis
\begin{flushleft}
\begin{figure*}
\begin{center}

  \includegraphics[trim = 1mm 10mm 8mm 18mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_regions_percolation.pdf}
  \includegraphics[trim = 0mm 00mm 00mm 00mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_regions_volume.pdf}

  \captionof{figure}{\small Percolation analysis of void regions for 
  different $\lambda_{th}$ values and for both defined classification 
  schemes. T-web (blue lines) and  V-web (green lines). Plot of the largest 
  volume and the number of voids detected according to the threshold value 
  $\lambda_{th}$ (left panels). Size distribution histogram of void cells
  using the threshold value $\lambda_{th} = 0.0$ for both schemes 
  (right panel).}

  \label{fig:percolation_analysis}
  \vspace{0.1 cm}

\end{center}
\end{figure*}
\end{flushleft}
%.........................................................................

%.........................................................................
%FIGURE 4: Distribution of eigenvalues of the inertia tensor
\begin{flushleft}
\begin{figure}
\begin{center}

  \includegraphics[trim = 7mm 9mm 1mm 0mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_inertia_tensor_Tweb}
  \includegraphics[trim = 7mm 9mm 1mm 0mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_inertia_tensor_Vweb}

  \captionof{figure}{\small Histogram of eigenvalue ratio $\tau_1/\tau_2$
  vs $\tau_2/\tau_3$ for the inertia tensor of void regions. T-web 
  (upper panel) and V-web (lower panel). Number of cells per 
  region in 2D histograms are indicated by the respective colour bar. 
  Upper ($\tau_1/\tau_2$) and right ($\tau_2/\tau_3$) panels of each 
  figure shows a normalized histogram of each ratio parameter. The 
  adopted division for quantify the morphology of void regions is not
  well justified, it should be understood as a fuzzy and continuous 
  limit, done just for illustrative purposes.}

  \label{fig:distro_inertia}
  \vspace{0.1 cm}

\end{center}
\end{figure}
\end{flushleft}
%.........................................................................

%.........................................................................
\end{document}

>>>>

Once defined the numerical details about both classification schemes, we
shall analyse the dependence on the threshold value $\lambda_{th}$ for 
each one. For this, we shall use the distribution of dark matter halos as 
tracer of the underlying matter field in order to be more consistent with
available observational data. In Figure \ref{fig:halos_fractions} we 
calculate fractions of halos within each one of the defined environments 
based upon the FOF catalogue of the simulation and for an extensive \lth 
range. Then we look for some key feature that could indicated us a 
possible optimal value of the \lth value. One first step forward our quest 
is the behaviour of the V-web scheme compared with the T-web. As was 
previously established by \SRKED{Hoffman et al. (2012)} and as can be seen 
in Figure \ref{fig:halos_fractions}, V-web scheme is significantly more 
sensible to variations of the $\lambda_{th}$ value, since all fractions of
halos for the V-web change significantly in the range $[0,0.4]$, whereas, 
for the T-web scheme, fractions change smoothly throughout all \lth range 
covered. From this, it is then expected that the optimal \lth value for the 
V-web scheme is less than the T-web value.

The more notorious characteristic of Figure \ref{fig:halos_fractions} is
the behaviour of the fraction of halos within sheet regions for both web 
schemes, increasing until a local maximum, and then decreasing. The 
increasing or decreasing rate of the fraction of halos for some region 
could be interpreted as a measure of the degree of non-linearity of such 
region for some specific \lth value. For example, filaments and knots, 
that are the most non-linear regions of the universe, have a negative rate 
for all covered \lth range. In the case of voids, the situation is 
completely opposite, where fractions of halos increase in everywhere. If 
we think in terms of the underlying matter field of the cosmic web, \lth 
is just a cutting parameter between high non-linear regions (filament and 
knots) and low non-linear (voids and sheets). Furthermore, if we take into 
account that dark matter halos are much more likely to form in high 
non-linear regions, it is expected the obtained behaviour of fractions of 
halos for voids, filaments and knots as we increase the \lth value. 
However, the behaviour of the fraction of halos in sheets is less clear,
increasing for low \lth values (like voids) and decreasing for higher \lth 
values (like filaments and knots). This indicates us the transitional 
character of sheet regions in the cosmic web. Our proposal here is to 
select as optimal \lth the value where the fraction of sheets reaches a
local maximum, so sheets are completely taken as intermediate transitional 
and neutral zones regarding the degree of non-linearity. According to this,
we find for the T-web scheme a optimal value $\lambda_{opt}^T = 0.36$ and
for the V-web scheme $\lambda_{opt}^V = 0.20$. In figure 
\ref{fig:visual_impression} we show the visual impression of the cosmic 
web along with the density field for different \lth values including the 
optimal values.

@@

%.........................................................................
%FIGURE 1: Fraction of halos in each environment
\begin{flushleft}
\begin{figure}
\centering

  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/halos_fraction_FOF_Tweb.pdf}

  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/halos_fraction_FOF_Vweb.pdf}

@@

  \label{fig:halos_fractions}
  \vspace{0.1 cm}

\end{figure}
\end{flushleft}
%.........................................................................

%.........................................................................
%FIGURE 2: Visual impression of the cosmic web
\begin{flushleft}
\begin{figure*}
\centering

  \captionof{figure}{\small Visual impression of the density field (left 
  panels), and of each classification scheme with the $\lambda_{th}$ values 
  obtained by our criteria (others panels). The color convention for each 
  environment is (white) - void, (light gray) - sheet, (gray) - filament, 
  (black) - knot. For each web scheme, it has been used the previously 
  established optimal threshold as a reference value, so plots are done 
  with the next values $\lambda_{th} = 0.0$, $\lambda_{th} = 
  \lambda_{opt}/2$, $\lambda_{th} = \lambda_{opt}$ and $\lambda_{th} = 
  2\lambda_{opt}$.}

@@

\end{document}
